%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Work Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{C++ computer vision developper : 3D solutions for digital dentistry.}% Job title
{Dental Wings/Straumann Group, Digital Business Unit} % Organization
{Montréal, CANADA} % Location
{Dec. 2016 - PRESENT} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Algorithms for optical calibration, 3D scanning/reconstruction, dental metrology,  with state of the art technology.}
\subitem {Prototyping in Python (Numpy, plotly, jupyter notebooks)}
\subitem {Agile development in C++ (OpenCV, Ceres, Eigen, Boost)}
\subitem {Building and versioning (VS 2017, Git)}
\item {Conception of a virtual scanner for hardware/software experimentation and validation.}
\item {Camera (and other devices) hardware validation. CMOS and camera integration.}
\item Conferences attendance (CVPR 2018, Agile Tour 2017), open days for recruiting interns (Concordia university, Polytechnique, McGill).
\end{cvitems}
}

%------------------------------------------------  

\cventry
{Research assistant \textbf{(*)} : Graph-based estimation of probe trajectory for sensorless freehand 3D US.}% Job title
{LATIS, ÉTS Montréal} % Organization
{Montréal, CANADA} % Location
{Jan. 2015 - Nov. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Calibration of optical and electromagnetic probes for freehand 3D US.}
\subitem {Development in C++ (3rd party lib, SVN) and compilation (CMake).}
\item {Image registration from echographic sequence using speckle-decorrelation. Trajectory estimation by a directed graph with uncertainty (gaussian process regression and Lie Algebra). \url{https://link.springer.com/chapter/10.1007/978-3-319-47157-0_25}}
\subitem {Programming in C/C++ (GSL, OpenCV, Boost, Eigen), compilation under GNU/Linux (make)}
\subitem {Quantitative and qualitative analysis (MATLAB)}
\item {Poster presentation at Colloque REPARTI 2016. Accepted paper for MICCAI/MLMI 2016 conference.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Intern \textbf{(*)} : Fast initialization of cartesian track using FM band} % Job title
{Thales Group, Thales Air Systems} % Organization
{Limours, FRANCE} % Location
{Feb. 2014 - Aug. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Track initialization in cartesian coordinates with range measurements, using a custom non-linear filter and statistical methods.}
\subitem {Implementation on MATLAB.}
\item {Validation on aircraft records.}
\subitem {Validation on MATLAB (MEX function) and C++ (Eigen).}
\end{cvitems}
}
\vspace{10mm}
\end{cventries}
