%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Relevant Projects}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{} % Affiliation/role
{} % Organization/group
{} % Location
{} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\vspace{-5mm}
\begin{cvitems}
\item {Blog about computer science (html, jupyter notebooks). \url{https://ltetrel.github.io/}.}
\item {Automatic row counting for kniting. Image processing and edge detectors (Python).}
\item {Stock market indicator analysis for best investment (Matlab, TensorFlow).}
\item {Design of an autonomous robot's detection system for an international competition. Programming (C) and PCB design (Altium).}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Shool projects} % Affiliation/role
{McGill, ÉTS Montréal} % Organization/group
{Montréal, CANADA} % Location
{2014 - 2016} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Registration of MRI and CT images using Gaussian Process interpolation with uncertainty.}
\item {GPGPU and GPU architecture introduction, Sobel filtering development using CUDA (NPP) on Nvidia GTX.}
\item {Automatic classification and prediction models for early Parkinson disease. Features extracted from MRI images of patient's brain.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Shool project manager : Business creation simulation for electronic shoes.} % Affiliation/role
{Lyon INSA} % Organization/group
{Lyon, FRANCE} % Location
{Sept. 2012 - Jun. 2013} % Date(s)
{ % Description(s) of experience/contributions/knowledge
\begin{cvitems}
\item {Team management of 10 people with establishment of project plan, functional analysis and marketing mix.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
