%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Publications, Conferences \& Awards}

%------------------------------------------------

\begin{cvhonors}
	
\cvhonor
{OHBM} % Award
{${^1}$ \label{award:1} Fast and accurate EPI spatial normalization using convolutional neural network (poster 2325)} % Event
{Online} % Location
{Jun, 2021}

\cvhonor
{NeuroImage} % Award
{${^3}$ \label{award:3} \url{https://www.sciencedirect.com/science/article/pii/S1053811921001245}} % Event
{Online} % Location
{May, 2021}

\cvhonor
{OHBM} % Award
{${^4}$ \label{award:4} NeuroLibre : A cloud-based and curated repository for Jupyter Notebooks in neurosci. (poster 1902)} % Event
{Online} % Location
{Jun, 2020}

\cvhonor
{Courtois Neuromod event} % Award
{${^2}$ \label{award:2} Benchmarking 3D-CNN models for brain decoding on CPU servers.} % Event
{\hspace{-5mm}Montréal (QC), CANADA} % Location
{Feb, 2020}

\cvhonor
{CVPR} % Award
{Promoting computer vision research for Staumann.} % Event
{\hspace{-5mm}Salt Lake city (UT), USA} % Location
{Jun, 2018} % Date(s)

\cvhonor
{Agile Tour} % Award
{Training for agile development.} % Event
{\hspace{-5mm}Montréal (QC), CANADA} % Location
{Nov, 2017} % Date(s)

\cvhonor
{Grant} % Award
{Bourse interne ÉTS : merit scholarship for graduate students (3.000 CAD).} % Event
{\hspace{-5mm}Montréal (QC), CANADA} % Location
{Mar, 2016} % Date(s)

\cvhonor
{MICCAI} % Award
{$^6$ \label{award:6} \url{https://link.springer.com/chapter/10.1007/978-3-319-47157-0_25}} % Event
{Athens, GREECE} % Location
{Oct, 2016} % Date(s)

\cvhonor
{Master thesis} % Award
{$^5$ \label{award:5} \url{https://espace.etsmtl.ca/id/eprint/1753/}} % Event
{\hspace{-5mm}Montréal (QC), CANADA} % Location
{Aug, 2016} % Date(s)

\cvhonor
{24h de l'innovation (1st place)} % Award
{Mobile app to teach science for children.} % Event
{\hspace{-5mm}Montréal (QC), CANADA} % Location
{May, 2015} % Date(s)

%------------------------------------------------

\cvhonor
{Explora'sup grant} % Award
{Regional merit scholarship for undergraduate students (2.000 EUR).} % Event
{Lyon, FRANCE} % Location
{Aug, 2014} % Date(s)

\cvhonor
{Eurobot (qualification phase)} % Award
{International robotic contest with autonomous robots.} % Event
{La Ferté B., FRANCE} % Location
{May, 2013} % Date(s)

\end{cvhonors}
