%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Work Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}


%------------------------------------------------

\cventry
{Data Science Engineer: Academic research}% Job title
{SIMEXP lab, CRIUGM - University of Montreal (UdeM)} % Organization
{\hspace{-5mm}Montréal (QC), CANADA} % Location
{Nov. 2018 - PRESENT} % Date(s)
{ % Description(s) of tasks/responsibilities
	\begin{cvitems}
		\item {Software tools for neuroimaging research. \url{https://github.com/SIMEXP}}
		\subitem {HPC Scalable fMRI preprocessing and quality-control on BIDS datasets for CCNA (fMRIPrep, SLURM, Datalad)}
		\subitem {fMRIPrep Long-term Support and reproducibility testing (Datalad, SLURM)}
		\item {Machine learning for applied neuroimaging research.}
		\subitem {\hyperref[award:1]{$^1$} Fast and accurate fMRI registration with quaternions using convolutional neural network (Tensorflow)}
		\subitem {\hyperref[award:2]{$^2$} Intel collaboration on CPU and GPU HPC distributed training for brain-state annotation (Horovod, SLURM)}
		\subitem {\hyperref[award:3]{$^3$} Graph convolution network and feature visualization for  brain-state annotation (PyTorch, Tensorflow)}
		\item {CONP-Neurolibre: \hyperref[award:4]{$^4$} open and interactive neuroscience notebooks on the cloud. \url{https://binder.conp.cloud/}}
		\subitem {Server administrator for the McGill Kubernetes cluster (Binderhub, openstack, terraform, Docker)}
		\item {Communication (oral presentations, hackaton trainer, student support), open-science practices and contributions (Nilearn, Binderhub)}
		\item {Conferences attendance (MAIN 2018-19-20, OHBM 2019-20-21)}
	\end{cvitems}
}

%------------------------------------------------

\cventry
{Computer Vision Developer\textbf{*}: 3D solutions for digital dentistry.}% Job title
{Dental Wings/Straumann Group, Digital Business Unit} % Organization
{\hspace{-5mm}Montréal (QC), CANADA} % Location
{Dec. 2016 - Oct. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {3D reconstruction algorithms}
\subitem {State of the art research on stereoscopy using phase-shift model (C++, Ceres, Eigen)}
\subitem {Optical calibration (openCV, Ceres) and distorsion correction (Python)}
\subitem {Metrology reports and software documentation}
\subitem {Conception of a virtual scanner for software experimentation and hardware validation (Blender)}
\item {Conferences attendance (CVPR 2018, Agile Tour 2017), open days for recruiting interns (Concordia, Polytechnique, McGill)}
\end{cvitems}
}

%------------------------------------------------  

\cventry
{Research assistant\textbf{*} : Graph-based estimation of probe trajectory for sensorless freehand 3D US.}% Job title
{LATIS, ÉTS Montréal} % Organization
{\hspace{-5mm}Montréal (QC), CANADA} % Location
{Jan. 2015 - Nov. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Calibration of optical and electromagnetic probes for freehand 3D US (C++, PLUS, SVN, CMake)}
\item {\hyperref[award:5]{$^5$} Master thesis: \hyperref[award:6]{$^6$} Sensorless image reconstruction for ultrasound}
\subitem {Image registration from echographic sequence using speckle-decorrelation (C, GSL, Make)}
\subitem {Trajectory estimation by a directed graph with gaussian process uncertainty and Lie Algebra (Matlab, C++, Boost, Eigen)}
\item {Conferences attendance (REPARTI 2016, MICCAI/MLMI 2016)}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Intern\textbf{*} : Fast initialization of cartesian track using FM band} % Job title
{Thales Group, Thales Air Systems} % Organization
{Limours, FRANCE} % Location
{Feb. 2014 - Aug. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Track initialization in cartesian coordinates with range measurements, using a custom non-linear filter and statistical methods (MATLAB)}
\subitem {Validation on aircraft records (MATLAB MEX, C++, Eigen)}
\end{cvitems}
}
\end{cventries}
